\section{Taxis Protocol}
\label{sec:protocol}

In this section we present a new protocol \Taxis and its basic building blocks.
%
The ultimate product of \Taxis is a ledger \ledger providing fair transaction order.

Before we introduce \Taxis, we present its preliminary version \TaxisWL as a direct comparison with \textsf{Aequitas}.
%
\TaxisWL achieves consistency, weak-liveness and $(\varphi, \DBW)$-order-fairness.
%
Specifically, while the liveness is weak (same as \textsf{Aequitas}), this protocol achieves the best transaction order fairness that we can expect.
%
Next, by adding a few simple modifications on \TaxisWL, we present \Taxis that reconciles the tension between liveness and fair order.
%
The ledger of \Taxis satisfies consistency, (standard) liveness and $(\varphi, \TDBW)$-fair-order.

\Taxis is a two-stage protocol that decouples the mining procedure of profiles and the final serialization of transactions.
%
We will use blockchain as an intermediate information aggregator to collect profiles (i.e., transaction log) and build the ultimate ledger \ledger on top of this blockchain.
%
For simplicity, we present \TaxisWL and \Taxis assuming static number of participants and discuss how to adapt them to the dynamic participation in \cref{subsec:dynamic-participation}.

\paragraph{Blockchain notations.}
%
A block with target $T \in \mathbb{N}$ is a quadruple of the form $\block = \langle ctr, r, h, x \rangle$ where $ctr, r \in \mathbb{N}$, $h \in \{0, 1\}$ and $x \in \{0, 1\}^*$.
%
A blockchain \chain is a (possibly empty) sequence of blocks; the rightmost block by convention is denoted by \chainHead{\chain} (note $\chainHead{\varepsilon} = \varepsilon$).
%
These blocks are chained in the sense that if $\block_{i + 1} = \langle ctr, r, h, x \rangle$, then $h = H(\block_i)$, where $H(\cdot)$ is cryptographic hash function with output in $\{0, 1\}^\kappa$.
%
We adopt \timestamp{\block} to denote the timestamp of \block; and, slightly abusing the notations and omitting the current time \round, we will use $\chain^{\lceil k}$ to denote the chain from pruning all blocks \block such that $\timestamp{\block} \ge \round - k$.

\paragraph{2-for-1 proof-of-Work.}
%
2-for-1 PoW is a primitive that binds multiple PoW mining processes together by utilizing a single random oracle query.
%
It was first proposed in \cite{EC:GarKiaLeo15} to improve the corruption threshold in ledger consensus.
%
This primitive mitigates the possible attack with multiple independent mining processes, where the adversary can join forces to any one of the oracles and gain undesired advantage.

We will use 2-for-1 PoW to mine two types of blocks: ledger blocks and profile blocks.
%
Ledger blocks form the \Taxis blockchain and they will only include recent profile blocks (unlike regular blockchains, ledger blocks in \Taxis will not include any transactions ``directly'').
%
Meanwhile, parties will use profile blocks to report their local profiles.
%
We denote the mining target of ledger blocks and profile blocks by $T_\LB$ and $T_\PB$, respectively.
%
\Taxis will maintain a constant ratio between them; for simplicity, in our presentation and analysis, we assume $T_\LB = T_\PB$.

The main goal of adopting 2-for-1 PoW to bind the mining process of these two types of blocks together, is to achieve better \emph{chain quality}.
%
Recall that chain quality is bad in the Bitcoin backbone protocol \cite{EC:GarKiaLeo15,C:GarKiaLeo17}, where the adversary can contribute more blocks to the common prefix compared with her relative computational power.
%
By adopting 2-for-1 PoW, \Taxis guarantees that, for a sufficiently long time, $\varphi$ fraction of parties mine $\varphi$ fraction of the profiles (and they are all included by ledger blocks in the blockchain).

\paragraph{Freshness and recency parameter.}
%
For the sake of achieving better chain quality on profile blocks, certain changes should be made to the 2-for-1 mining procedure.
%
Ideally, the adversary \adv should not be allowed to mine profile blocks timestamped in the very future; and, blocks should go stale as time passes by so that \adv cannot choose to withhold them to gain a sudden advantage.
%
Analogous to the treatment in fruitchain \cite{PODC:PasShi17}, we introduce two mechanisms to help ensure the \emph{freshness} of profile blocks.
%
On one hand, the header of a profile block should point to the last block in the settled blockchain; this prevents the adversary from mining blocks in the very future, as an honest ledger block will introduce fresh randomness which is unpredictable for \adv.
%
On the other hand, we set a recency parameter $R$ (in rounds) such that a profile block \PB referring to a settled ledger block \LB will only be valid before time $\timestamp{\LB} + R$ (in other words, it cannot be included by a ledger block with timestamp later than $\timestamp{\LB} + R$).

\input{content/protocol/taxiswl}
\input{content/protocol/taxis}
\input{content/protocol/taxis-dynamic}
