\subsection{Taxis with Dynamic Participation}
\label{subsec:dynamic-participation}

We detail how to adapt the above two protocols \TaxisWL and \Taxis from static number of parties to the dynamic participation.

\paragraph{Difficulty recalculation function.}
%
In a permissionless environment, mining difficulties $T_\LB$ and $T_\PB$ should be adjusted as the participant population fluctuates.
%
We adopt the same difficulty adjustment function in Bitcoin\footnote{We refer to \cite{C:GarKiaLeo17} for more details on analysis of Bitcoin with dynamic participation.} to recalculate $T_\LB$ (so $T_\PB$ is adjusted as well).
%
More specifically, this function adjusts mining difficulty at the end of epochs (an epoch consists of $m$ blocks), and the target for the next epoch $T'_\LB$ is computed base on current target $T_\LB$ and the time elapsed to mine $m$ blocks --- i.e., $T'_\LB = \varLambda / (m / f) \cdot T_\LB$ where $f$ is the ideal block generation rate, and $\varLambda$ is the difference between the timestamps of the last block in the previous and current epoch.
%
In addition, the relative amount of difficulty that can be adjusted each time is bounded by a constant $\tau$ (which is similar to that in Bitcoin where $\tau = 4$ is in use).

\paragraph{Counting majority as accumulated difficulty.}
%
Note that after profile blocks are mined under different difficulties, we should count ``majority'' in a \PBWindowLen-time-window in a new sense.
%
Precisely, we say some blocks account for the majority if they accumulate more than $d / 2$ difficulty where $d$ is the total difficulty of all profile blocks in the time window.
%
This new majority rule applies to building graph stage in \cref{algorithm:taxiswl-extract-transaction-order,algorithm:taxis-extract-transaction-order}.
%
It also applies to the selection of median timestamps.
%
I.e., a timestamp $t$ is selected for \tx because $t$ is the earliest timestamp such that all profiles that report a timestamp no later than $t$ yields more than half of the accumulated difficulties in \tx's \PBWindowLen-time-window.
